\LaTeXe\ guide for the Journal of Functional Programming

### 2019-10-22 papers/jfp/7-experience.tex
Reword the paragraph on cloud Hadrian

The subsequent development of \Cloud \Shake allows GHC developers to take advantage of
sharing build results between builds, which is particularly promising in the
context of GHC's continuous integration (CI) infrastructure responsible for
building and testing every GHC commit. Building GHC~8.8 from scratch with
default settings takes around 1 hour on Windows using either \Hadrian or the
original \Make-based build system. This time includes building the compiler itself,
29~bundled libraries, such as \cmd{base} (each in vanilla and profiled way), and
6~bundled executables, such as \cmd{Haddock}. A single commit typically modifies
only a small part of the whole codebase, making the cloud-build functionality
highly desirable. For example, if a commit does not touch any GHC source files
(e.g. only modifies the documentation), \Hadrian can build GHC from scratch in under
3~minutes, by simply creating symbolic links to the previously built results
stored in the \Cloud~\Shake cache.

>>>>

The development of \Cloud \Shake allows GHC developers to benefit from caching
build results between builds. Building GHC~8.8 from scratch takes $\sim$1~hour
on Windows using \Hadrian or the original \Make-based build system. This time
includes building the compiler itself, 29~bundled libraries, such as \cmd{base}
(each in vanilla and profiled way), and 6~bundled executables, such as
\cmd{Haddock}. One would hope that the build cache would be particularly useful
for GHC's continuous integration system that builds and tests every commit but
our experience has been mixed. In an ideal case, when a commit does not affect
the resulting GHC binaries, e.g. only modifies tests, \Hadrian can build GHC
from scratch in just 3~minutes, by simply creating symbolic links to the
previously built results stored in the cache. However, if a commit modifies the
``Stage 1 GHC'' executable -- an intermediate compiler built as part of the GHC
bootstrapping -- any further cache hits become unlikely, thus limiting
benefits of the build cache to Stage 1 only~\cite{cloud_hadrian}.
